Tracing the Meta-Level: PyPy's Tracing JIT Compiler

### 2009-04-02 talk/icooolps2009/paper.tex
kill these comments, as I am not going to act on them
mark an unclear sentence, and some rewording

A recent approach to getting better performance for dynamic languages is that of
tracing JIT compilers \cite{XXX}. Writing a tracing JIT compiler is relatively
simple, because it can be added to an existing interpreter for a language,
because the interpreter takes over some of the functionality of the compiler and
the machine code generation part can be simplified.

@@

The operations in this sequence are operations of the mentioned intermediate
representation (e.g. note that the generic modulo and equality operations in the
function above have been recognized to always work on integers and are thus
rendered as \texttt{int\_mod} and \texttt{int\_eq}). The trace contains all the
operations that were executed, is in SSA-form \cite{XXX} and ends with a jump
to its own beginning, forming an endless loop that can only be left via a guard
failure. The call to \texttt{f} was inlined into the trace. Of the condition in
\texttt{f} the much more common \texttt{else} case was traced. The other case is
implemented via a guard failure. This trace can then be turned into machine code
and executed.

@@

\anto{XXX: should we say that virtualizables are very cool, that nobody else
  does that and that they are vital to get good performaces with python
  without sacrificing compatibility?} \cfbolz{no: feels a bit dishonest to not
  describe them properly and then say that they are very cool and vital}

>>>>

A recent approach to getting better performance for dynamic languages is that of
tracing JIT compilers \cite{XXX}. Writing a tracing JIT compiler is relatively
simple, because it can be added to an existing interpreter for a language,
because the interpreter takes over some of the functionality of the compiler and
the machine code generation part can be simplified.
\anto{XXX small english issue: I don't like the two consecutive ``because'',
  I'm not even sure what is the right way to interpret the sentence}

@@

The operations in this sequence are operations of the mentioned intermediate
representation (e.g. note that the generic modulo and equality operations in the
function above have been recognized to always work on integers and are thus
rendered as \texttt{int\_mod} and \texttt{int\_eq}). The trace contains all the
operations that were executed, is in SSA-form \cite{XXX} and ends with a jump
to its own beginning, forming an endless loop that can only be left via a guard
failure. The call to \texttt{f} was inlined into the trace. \sout{Of the condition in
\texttt{f} the much more common \texttt{else} case was traced. The other case is
implemented via a guard failure. This trace can then be turned into machine code
and executed.}
\anto{
Note that the trace contains only the hot \texttt{else} case of the
\texttt{if} test in \texttt{f}, while the other branch is implemented via a
guard failure. This trace can then be turned into machine code and executed.
}

@@
